---
title: "Estimating knots in BLSGMs w/o(w) TICs in the framework of individual measurement occasions"
author: Jin Liu
output: rmarkdown::github_document
date: 2020/12/21
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## OS, R version and OpenMx Version
```{r}
OpenMx::mxVersion()
```

## Require package would be used
```{r}
library(tidyr)
library(ggplot2)
```

## Data set with positve knot variance
### Read in dataset for analyses (wide-format data)
```{r}
dat <- read.csv(file = "Correctly_specified_knot_variance/example_data.csv")
```

### Summarize data
```{r}
summary(dat)
```

### Visualize data
```{r}
long_dat_T <- gather(dat, var.T, time, T1:T10)
long_dat_Y <- gather(dat, var.Y, measures, Y1:Y10)
long_dat <- data.frame(id = long_dat_T[, 1], time = long_dat_T[, 15],
                       measures = long_dat_Y[, 15])
ggplot(aes(x = time, y = measures), data = long_dat) +
  geom_line(aes(group = id), color = "lightgrey") +
  geom_point(aes(group = id), color = "darkgrey", size = 0.5) +
  geom_smooth(aes(group = 1), size = 1.8, col = "lightblue", se = F) + 
  labs(title = "Nonlinear Pattern with Individually Varying Measurement Time",
       x ="Time", y = "Measurement") + 
  theme(plot.title = element_text(hjust = 0.5))
```

### Bilinear Spline Growth Model with an Unknown Fixed Knot
```{r, message = F}
source("Correctly_specified_knot_variance/BLSGM_fixed.R")
out
```

### Bilinear Spline Growth Model with an Unknown Random Knot 
```{r, message = F}
source("Correctly_specified_knot_variance/BLSGM_random.R")
out
```

### Bilinear Spline Growth Model with an Unknown Random Knot (constraint)
```{r, message = F}
source("Correctly_specified_knot_variance/BLSGM_random_constraint.R")
out
```

### Bilinear Spline Growth Model-TICs with an Unknown Fixed Knot
```{r, message = F}
source("Correctly_specified_knot_variance/BLSGM_TICs_fixed.R")
out
```

### Bilinear Spline Growth Model-TICs with an Unknown Random Knot
```{r, message = F}
source("Correctly_specified_knot_variance/BLSGM_TICs_random.R")
out
```

### Bilinear Spline Growth Model-TICs with an Unknown Random Knot (constraint)
```{r, message = F}
source("Correctly_specified_knot_variance/BLSGM_TICs_random_constraint.R")
out
```

## Data set with zero knot variance
### Read in dataset for analyses (wide-format data)
```{r}
dat <- read.csv(file = "Over_specified_knot_variance/example_data.csv")
```

### Summarize data
```{r}
summary(dat)
```

### Visualize data
```{r}
long_dat_T <- gather(dat, var.T, time, T1:T10)
long_dat_Y <- gather(dat, var.Y, measures, Y1:Y10)
long_dat <- data.frame(id = long_dat_T[, 1], time = long_dat_T[, 15],
                       measures = long_dat_Y[, 15])
ggplot(aes(x = time, y = measures), data = long_dat) +
  geom_line(aes(group = id), color = "lightgrey") +
  geom_point(aes(group = id), color = "darkgrey", size = 0.5) +
  geom_smooth(aes(group = 1), size = 1.8, col = "lightblue", se = F) + 
  labs(title = "Nonlinear Pattern with Individually Varying Measurement Time",
       x ="Time", y = "Measurement") + 
  theme(plot.title = element_text(hjust = 0.5))
```

### Bilinear Spline Growth Model with an Unknown Fixed Knot
```{r, message = F}
source("Over_specified_knot_variance/BLSGM_fixed.R")
out
```

### Bilinear Spline Growth Model with an Unknown Random Knot 
```{r, message = F}
source("Over_specified_knot_variance/BLSGM_random.R")
out
```

### Bilinear Spline Growth Model with an Unknown Random Knot (constraint)
```{r, message = F}
source("Over_specified_knot_variance/BLSGM_random_constraint.R")
out
```

### Bilinear Spline Growth Model-TICs with an Unknown Fixed Knot
```{r, message = F}
source("Over_specified_knot_variance/BLSGM_TICs_fixed.R")
out
```

### Bilinear Spline Growth Model-TICs with an Unknown Random Knot
```{r, message = F}
source("Over_specified_knot_variance/BLSGM_TICs_random.R")
out
```

### Bilinear Spline Growth Model-TICs with an Unknown Random Knot (constraint)
```{r, message = F}
source("Over_specified_knot_variance/BLSGM_TICs_random_constraint.R")
out
```
